DOM bridges and barriers: systematic review and survey

### 2025-10-08 reports/draft_results.qmd
update figs

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 5.5
#| fig-align: center

@@

#stacked bar plots
ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    theme(legend.position = "right")+
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

#stacked bar plots
ggplot(freq_job_lit2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    theme(legend.position = "right")+
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

#stacked bar plots
ggplot(freq_pos_survey2, aes(fill=code_level, y=value, x=position)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    theme(legend.position = "top")+
    xlab("") + 
    ylab("Proportion of theme (%)")+
    theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))

>>>>

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 5
#| fig-align: center

@@

#stacked bar plots
ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black"))+
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

#stacked bar plots
ggplot(freq_job_lit2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification = "left", 
          legend.text = element_text(size = 14, color = "black")) +
    xlab("") + 
    ylab("Proportion of theme (%)")

@@

#stacked bar plots
ggplot(freq_pos_survey2, aes(fill=code_level, y=value, x=position)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "") +
    theme_ms() +
    theme(legend.position = "top", 
          legend.justification.top = "left", 
          legend.title = element_text(size = 16, color = "black"), 
          legend.text = element_text(size = 14, color = "black"))+
    guides(fill=guide_legend(nrow=2,byrow=TRUE))+
    xlab("") + 
    ylab("Proportion of theme (%)")+
    theme(axis.text.x = element_text(size = 14, color = "black", angle = 60, hjust = 1))
